% Acknowledgments must be written in complete sentences. Do not use direct address. For example, instead of "Thanks, Mom and Dad!", you should say "I thank my parents".
% Cameo
% Mrs. G
% PGC team, Mayar, including Art Alex
% Hoda - the way of the Essentialist
% Jen and Sarah for sharing their sanctuaries with me during the final days of writing my thesis.
% Pam
% Editor Anna Pardo
% Jennifer: teaching me long division.
% Mark: 
% Xunwu:
% Hualin Mei:
% Grandmommy and Granddaddy
% Carina: breathing exercises and monitors, and Wim!
% Soham and Ioannis (IN GREEK)
% Shubha
% Sikivie
% Tankaboy
% Kayla Rynor
% Sandy
Without so many two- and four-legged blessings along the way, I could never have made it to this point in my academic career.
Thus, I begin by giving my endless gratitude to my high energy physics mentors, Professors Andrey Korytov and Guenkah Mitselmakher, for granting me this one-of-a-kind opportunity to do real \emph{science} at CERN.

To my wife, Suzanne Rosenzweig, for showing me that dreams \emph{do} come true.
To my mother and father, Vicki and John, who always reassured me that I could achieve anything I put my mind to. Sleep peacefully, Mom.
To my siblings, Alex, Ryan, Devin, Jace, and Claudia who frequently and gently reminded me that life existed outside of grad school.
To Auntie Rachel and Uncle Yuri, who just \emph{get} me and have given to me everything I could have possible asked for. % TODO: UPDATE this line.
To my mentor, Sheldon Friedman, and his wife, Rita Friedman (Rosenzweig), who chose to invest in my success at a young age.
I have only made it this far thanks to their undying encouragement, love, and optimism.
To Sheldon's best friend, Dr. Bernard Khoury, whose reputation and has helped pave my own path.
To the many moms who generously gave unconditional support during the darkest of times and unequivocal love during the brightest times:
Cyndi Reilly-Rogers, Dawn Hood, Margaret Sherrill, and Silet Wiley.

% TODO: Give him a VERY warm thank you.
To Dr. Filippo Errico for his focus, leadership, selflessness, and patience in leading the Higgs mass analysis.
To Dr. Lucien Lo for showing me the simplicity and beauty of Python in his typical laid-back way and for leading the dilepton analysis. % TODO.
To Dr. Noah Steinberg for showing me how majestically physics can be communicated from mind to mind.
To Dr. Darin Acosta, for spending many hours of physics discussion with me and the other students, who have helped us build our ``CMS Office Hours''
Ari Gonzalez, Cris Caballeros, Jeremiah Anglin, Sean Kent, 
Evan Koenig, Neha Rawal, Nik Menendez, John Rötter.  % Grad students.
To the gents who paved my way to and through the world of CMS, Brendan Regnery and Bhargav Joshi.
To my mentee, Matthew Dittrich, for accepting the baton of knowledge and making everything come full circle.

To my comrades for showing me what it takes to survive the core courses, Dr. Atool Divakarla, Dr. Brien O'Brendan, Dr. Donyell Guerrero, and Dr. Vladinar Martinez.
To Adamya Goyal for all his gentleness, humility, patience, and tutorage.
% Daniel Guerrero el hombre de hierro (Man of Iron)
To my Polish roommates in Saint-Genis-Pouilly for showing me what home away from home feels like: Bartoszek, Dziadziuś, Karolina, and Sandruśa.
To the boys who have been there since the beginning: Jish, Willis, The Shane, Zacman, Duck, and Marcus for their clever competition and continual camaraderie which has shaped me to this day.
% Bum3, RabidGoatMaster, Bias Logic, 

To Big Tree who stood as a symbol of strength, beauty, and life for centuries before us.
As Irma's wild whirring winds worsened, the cacophony of ripping roots resounded throughout the western corridor.
There I stood in that frozen moment---awestruck, speechless---watching her \emph{fall} helplessly towards the physics building.
What could have been a catastrophe of cataclysmic proportions was instead a gentle grazing against the north windows of NPB where, there, she was gracefully laid to rest.
% You showed me grace in death and a helplessness I have never felt before.

Finally, to Existence, for this unpredictable, unbelievable blip of an experience called Life.
